### 2022-03-23 paper2.tex
merge in paper 1 critiques and comments
Final committee edits

Previous research has greatly failed to distinguish between the activation of
information-seeking behaviors online and offline. Using theories of 1) social
support and 2) uses and gratifications theory I investigate the factors associated
with each vehicle type when on information-seeking vehicle: personal connection,
doctor, social networking site, online forum, and online search engine. Using
novel survey data of 948 Americans and their experience seeking out
information about the COVID-19 vaccines, I find little evidence that online
search is more utilized than seeking social support from personal network
connections or health professionals. I find evidence that the vehicles queried
in this survey are conceptually different and that the utilization of different
vehicles varies by demography and information sources. Finally, I find that
different sources of information exposure and information search vehicles hold real
world consequences through their associations with COVID-19 vaccination rates
and intentions, as information from a doctor increased the COVID-19 vaccination
uptake while receiving information from a Social Networking Site like Facebook
or Twitter was associated with lower odds of vaccination.

@@

\hypertarget{intro-1}{%
\section{Intro}\label{intro-1}}

@@

Information is especially important given the prominent trends of
misinformation, disinformation, and mistrust in traditional institutions
\citep{starbird19, kata10}. While no belief in false information can be thought of as
harmless \citep{douglas21} some discredited theories such as 'vaccines cause autism'
have major ramifications for both the individual and public health.
For example, a newfound public resistance to vaccination
against Measles by so-called 'anti-vaxxers' caused a 17\% increase in rates
worldwide in 2019. This increase killed  142,000 people, most of whom were
children under the age of five \citep{givetash19}. However, even in the ever-evolving
research agenda of misinformation and infodemiology \citep{eysenbach02}, much of the
research focuses on the 'push' or 'supply' side of information, like spaces where
individuals first encounter with conspiracy theories or other information
\citep{johnsonOnlineCompetitionPro2020, broniatowski_etal20}.
% TODO cite something else here

The lack of research in which vehicles are likely to be chosen when an
individual faces a need for information makes it difficult for policy makers to
propose effective information campaigns that promote the health and wellbeing of
individuals in our society. Even outside of the misinformation literature, much
of the research conducted in social networks and communication focus on senders,
influencers, and persuasion strategies 
\citep{mertonManifestLatentFunctions1968, katzPersonalInfluencePart1955, lazarsfeldPeopleChoice1944},
rather than on “the receiver as an active information seeker and processor." 
\citep{johnsonComprehensiveModelCancerRelated1993}
\citep[for an exception, see]{eysenbach09}.

I use the case of information around COVID-19 vaccinations to explore the
variation of usage of information search vehicles. In doing so, I seek to answer
how computer-mediated or interpersonal information-seeking strategies vary
across populations in their search for information about COVID-19 vaccinations
and investigate how these strategies affect vaccination uptake. Specifically, this article 
answers two research questions: (1) How do computer-mediated or interpersonal information-seeking
strategies vary across populations? (2) How does the information search vehicle utilized 
affect COVID-19 Vaccination uptake?

@@

However, informational support can also be sought outside of the social network
context, namely via computer-mediated information search tools such as the
process of “Googling”, or the utilization of internet search engines. 
As the online environment began penetrating all facets of
modern human life, it makes sense that performing online search has become one
of the most convenient vehicles for information search. Small
\citet{smallSomeoneTalk2017} showed that Graduate students often
confided in a "miscellaneous classmates encountered down the hall" (p.
176) instead of established and trusted confidants because they
simply were there at the right time. I theorize that online search engines
may be the most frictionless and costless mode of support. 
No social capital or relationship is necessary when choosing to utilize a search engine.

There are three computer-mediated vehicles I consider for this analysis: online
search engines like Google or Bing, posting questions on online forums like
subreddits or Facebook groups, and posting a status update online via Facebook
or Twitter. While the first two are largely anonymous and do not require a
personal network, the third is a unique hybrid between personal network
connections and online search.

@@

Adapting these facets of UGT and social support to my own case, I theorize that
online search allows for increased anonymity, a lowered social cost, and the
potential avoidance of embarrassment and other negative social interactions,
especially in the case on search engines. \citet{rainsCopingIllnessDigitally2018}
finds that patients tend to search for
technical information about an illness online but they then turn to their social
network for experiential information from others facing similar circumstances in
the case of cancer. The type of information sought is therefore important.
If specific expertise on a specific topic is desired by a searcher, they may
reach out to personal connections that they see as expert such as a doctor, or
if an individual distrusts the medical establishment, they may be more likely to
activate informational support among their social network or turn to online
groups that validate their worldview \citep{bogersHowSocialAre2014}. Finally, UGT and
Brasher's definition of social support \citeyearpar{brashersInformationSeekingAvoiding2002}
help us to theorize that the psychosocial needs like identity management or relational
maintenance of an individual may influence their chosen information search vehicle: 
when the informational need is related to forming and deepening social ties search 
is likely to be done from network ties.

@@

My analytic strategy proceeds in four steps. In Tables \ref{tab:table-1-ind}
\& \ref{tab:table-2-dep}, I present descriptive statistics for all study
variables, including variable ranges, means, and standard deviations. For this
paper, I rely heavily on logistic regression, modeled in \texttt{r}; specifically, I
fit a series of binomial generalized linear models with a logit link \citep{venables2002a},
otherwise known as logistic regression model \citep{hothorn2006handbook}.
This approach is appropriate because the data
are non-nested, cross-sectional data with binary independent variables. In Table \ref{tab:table-model-1}
\footnote{All tables in this paper were created with the modelsummary package in \texttt{r} 
\citep{modelsummary}},I fit a logistic regression model predicting
whether someone sought information about COVID-19 using their sources of
information (`Received info') as well as various demographic variables such as
age, education level and race. Figure \ref{fig:plot-model-1} then illustrates
the relationship between the coefficients and information-seeking.\footnote{Figures 
in this paper were all created using the \texttt{r} packages jtools \citep{jtools}
and ggplot2 \citep{wickham_etal, wickham11}}.
In Table \ref{tab:model-2-phi}, I disaggregate information-seeking behaviors by
investigating the difference in proportions of each of the 5 different avenues
of seeking information about COVID-19: from another person, from a doctor, on an
online forum, on a social networking site, or using an online search tool. I
investigate these differences through a phi coefficient \citep{warrens08}, otherwise
known as a mean square contingency coefficient, which is used to investigate the
degree of association between two binary variables.\footnote{To calculate the Phi
  Coefficient, I utilize the Psych \texttt{r} package \citep{psych}} I then investigate the
associations between my predictors and the five information search vehicles by
modelling a series of logistic regressions in Table \ref{tab:table-model-2}.
Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information exposure sources, information-seeking behaviors and
the choice to get vaccinated against COVID-19 through a logistic regression
model predicting Vaccination Outlook. Figure \ref{fig:plot-model-3} then
illustrates the relationship between the coefficients and vaccination outlook.

@@

\begin{figure}[h]
{\centering \includegraphics[width=0.8\linewidth]{figs/paper2/plot-model-1-1}}
\caption{What predicts someone intentionally searched for information, Plot of Coefficients?}\label{fig:plot-model-1}
\end{figure}

Table \ref{tab:table-model-1} provides the results of my logistic regression
analysis predicting whether someone sought information about COVID-19. These
initial results suggest similar results for each vehicle of information
delivery: each mode of receiving information whether from a doctor, a person,
the news, a social networking site, or an online forum, all increase the odds of
seeking out information. For example, respondents who had received information
from a doctor or other medical professional were 2.82 (odds ratio = \(exp(\beta k)\),
\emph{p} \textless{} 0.001) times more likely to seek out information over someone
who had not. Similarly, respondents who had received information from `a
person like friend, neighbor, or family member that [they] know' were 1.87
(\emph{p} \textless{} 0.001) times more likely to seek out information over 
someone who had not received information from a person like that. Interesting, 
those who had received information from an online discussion group, listserv,
or other online forum including a Facebook group or subreddit were 2.39 (\emph{p}
\textless{} 0.001) times more likely to search out more information than 
someone who had not. While most demographic variables do not seem to have a 
strong effect on whether someone sought out information about the COVID-19 
vaccine, a few key variables had strong associations.  Respondents who are 
older are more likely to seek information; The odds are about 3\% higher when 
age is equal to x + 1 relative to x, possibly indicating a generational effect
of information-seeking patterns (\emph{p} \textless{} 0.01). Additionally,
those who were more educated, that is those with an Associate's degree or higher,
were 1.58 more likely to seek additional information than those without the degree
(\emph{p} \textless{} 0.05). And finally, there is evidence to suggest that the Black or
African American sample was more likely to seek out information, specifically:
Blacks were 3.58 times more likely to seek out information over non-Blacks (\emph{p}
\textless{} 0.05). Figure \ref{fig:plot-model-1} illustrates the relationship
between the coefficients and information-seeking.

\hypertarget{information-search-vehicles}{%
\subsection{Information Search Vehicles}\label{information-search-vehicles}}

@@

To further investigate how people search for information, I asked those who had
sought information out intentionally, ``How did you look for information about
the COVID-19 vaccine?'' Because respondents could select as many responses as
applicable, each response is recorded as a dichotomous variable. Table
\ref{tab:table-1-ind} reveals differences in the prevalence of usage of the
various information-seeking vehicles: Around 40\% of the sample has inquired for
information from a doctor, a person, or using online search tool (44\%, 42\%, 41\%), while my
respondents used vehicles like online forums (27\%) and social networking sites (18\%)
to seek out information at significantly lower rates.

To investigate how each
Information Search Vehicle are related to each other using the Phi Coefficient
($\phi$) of binary association between each Information Search Vehicle pair.
The Phi coefficient can be interpreted like a correlation coefficient, with
numbers closer to -1 indicating a very strong negative relationship and those closer to 
positive 1 indicating a very strong positive relationship
(Warrens 2008). Table \ref{tab:model-2-phi} shows the results of these
coefficients. Out of the five information search vehicles investigated, there is
evidence that the vehicles are distinctly different concepts because most
coefficients fall under 0.3, the general cutoff for correlation
coefficients to indicate a relationship. There does seem to be a relationship
between Online Forums and Social Networking Sites, possibly due to an
individual's latent propensity to use online networks over in-person networks. These
coefficients indicate a weak relationship between any two vehicles of
information search and that respondents in my sample utilize each of these a
little bit differently.

I find that indeed the most common vehicles are 
asking a doctor, asking a friend, and asking a search engine which confirms
Hypthesis \ref{hyp:drgooglefriend}. However, because the vehicles 95\% confidence intervals 
in Table \ref{tab:table-1-ind}
are overlapping, I fail to find evidence for Hypothesis \ref{hyp:online-vs-network},
that using an online search engine was more commonplace than asking a friend.

@@

I conduct a separate logistic regression for each search vehicle in Table \ref{tab:table-model-2}. 
Modeling each response as a separate formula is useful for interpretation, but
there are important caveats: because each logistic regression is on a different
scale, one must not compare the magnitude of coefficients between models. We
can, however, use the direction and significance of the coefficients to draw
conclusions about these different forms of information search vehicles.

The first model in Table \ref{tab:table-model-2} predicts whether a
respondent sought information intentionally about COVID-19 vaccinations by
asking their doctor or another health professional. First and foremost, I find
that those who received information about COVID-19 vaccinations were
6.97 times more likely to seek out more information from their doctor than those who had
not (\emph{p} \textless{} 0.001). However, receiving information from other vehicles also
increased the odds of seeking out information from medical professions. Those who
received information from a person such as a friend or a relative were
2.23 times more likely to ask their doctor (\emph{p} \textless{} 0.001), while those who received
information from the news or television were 1.55 times more likely (\emph{p} \textless{} 0.01). 
I also find that those who received information from an online forum like a subreddit were 51\% 
more likely to ask their doctors than those who had not (\emph{p} \textless{} 0.05). 
Finally, respondents with an Associate's degree or higher were 72\%
more likely to ask their doctor for information on the COVID-19 vaccinations
than those who held less education (\emph{p} \textless{} 0.01).

@@

Searching for information using an online search engine such as Google or Bing
is theoretically the search vehicle with the least amount of social or cognitive
friction. Our descriptive statistics showed that not everyone used this vehicle,
with only 41\% of our sample (See Table \ref{tab:table-1-ind}) having sought
information about the COVID-19 vaccines using online search engines. My model
reveals interesting patterns to help explain the variation. As with previous
models, receiving information of any kind increase the odds of online search,
though to varying magnitudes (Doctor: 1.54 odds; Person: 1.44 odds; News or Television: 2.98 odds; 
Social Networking Site: 3.57 odds; Online Forum: 2 odds). I also find that older respondents
were more likely to search online, with each addition year aged to yield 3\%
higher odds of searching online (\emph{p} \textless{} 0.001). The most interesting variations
come from what decreases the odds of online search. First, those with an
Associate's degree or higher were 61\%
less likely to search online for questions about COVID-19 than those with less
educational attainment (\emph{p} \textless{} 0.001). In addition, I find that Hispanic-Latinos
had 44\% lower odds of searching online than non-Hispanics (\emph{p} \textless{} 0.05).

@@

Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information receiving and information-seeking behaviors and
the choice to get vaccinated against COVID-19 through a logistic regression
model predicting Vaccination Outlook. I find that receiving information from a
doctor or other medical profession is associated with 2.85 odds of choosing
to receive a COVID-19 vaccination (\emph{p} \textless{} 0.001) and that seeking 
information from a doctor also increases the odds of vaccination by 4 (\emph{p} \textless{} 0.001).
I find that my respondents who received information on a social networking site
like Facebook or Twitter about the vaccines were 55\%
\textbf{less likely} to choose to get vaccinated than those who received no information through
that vehicle (\emph{p} \textless{} 0.001). However, I did find that those who reached out to
family or friends with their concerns were 77\% more likely to become vaccinated 
(\emph{p} \textless{} 0.05). Furthermore, my respondents who held an Associate's degree
or above had 3.6 higher odds of becoming immunized (\emph{p} \textless{} 0.001).
And finally, I found further ethnoracial differences in my sample. I found that
Hispanic-Latinos had 2.83 higher odds of vaccination than non-Hispanics
(\emph{p} \textless{} 0.05) and that my Asian sample had 4.73 higher odds as well over
non-Asians (\emph{p}  = 0.09). See Figure \ref{fig:plot-model-3} for a visual
representation of how these different coefficients are related to vaccination outlook.

@@

Previous research in Sociology and Infodemiology has greatly failed to
distinguish between the activation of information-seeking behaviors online and
offline. In this paper, I sought to uncover just how different various methods of
information search are and begin a line of research inquiry that investigates
the factors associated with each different vehicle. Finally, I also uncovered
how the different sources of information exposure and information search
vehicles hold real world consequences through their associations with COVID-19
vaccination rates and intentions.

@@

Table \ref{tab:table-model-2} further demonstrated important takeaways about
how individuals seek information. First, I find that the different information
seeking vehicles queried in this survey are conceptually different and that the
utilization of different varies by demographic and information exposure source. 
Overall, being exposed to information about COVID-19 vaccinations from any 
source is associated with information-seeking behaviors,
though there are key variations. First, if one received information from a
doctor, they were likely to search from information from a doctor; this may
indicate an already existing trusting relationship between patient and
healthcare provider but it may also indicate the healthcare provider taking
initiative and emphasizing the importance of the vaccine or the survey respondent
seeking out information from an expert. Another important finding is that if you
received information from a Social Networking Site like Facebook or Twitter, you
were less likely to query Online Forums like Reddit or Facebook Groups; this may
be an example of Uses and Gratification Theory
\citep{blumlerUsesMassCommunications1974}, where the two online platforms may act as
substitute sources of information and those who were satisfied with the
information they received on a Social Networking Site didn't have the need to
seek out more information. Finally, the ethnoracial variations exhibited in
Table \ref{tab:table-model-2} likely demonstrate how cultural attitudes around
the trustworthiness of different sources of information affect the utilization
of different methods; for example, Asians seem are less likely to use online
forums than non-Asians, while Hispanics are more likely to use them than
non-Hispanics. The internal variations between the different information search
vehicles hint at different user profiles and may have major repercussions on the
quality of information they find and who is exposed to poor quality information.

Given the rampant misinformation around COVID-19, its related vaccinations
\citep{pathakInfodemicsCOVID19Role2020, mottaHowRightLeaningMedia2020, shahsavariConspiracyTimeCorona2020},
and the slowed rate of vaccinations in the
United States, it is important to uncover what relationship the different
sources of information exposure and information search vehicles for COVID-19 vaccinations
are associated with compliance with public health recommendations. Table
\ref{tab:table-model-3} demonstrated just how these different sources of information 
exposure and information search vehicles are associated with real world
consequences through COVID-19 vaccination rates and intentions. The first
takeaway is that receiving or seeking information from a doctor or other medical
profession was associated with higher likelihood of completed or planned vaccinations.
While blanket advice like ``Healthcare Providers should recommend the vaccine to
their patients'' would be ineffective because of the declining number of
Americans with a primary care doctor \citep{levine_etal20}, increasing trust in the
institution of medicine seems to remain a strong predictor of vaccinations.
A second major takeaway is that receiving information from a Social Networking
Site like Facebook timeline or Twitter status update was significantly
associated with lower vaccination rates. While we do not know what exact
information was absorbed on these platforms, the lower odds of vaccination
indicate that it was not positive. Much has been attempted between 2020 and 2022
to curb vaccine misinformation on these social networking platforms 
\citep[see][for an early example]{bowman20}; however, I find evidence that these social
networking platforms nevertheless have a measurable negative impact. Finally,
this study also contributes to the conversation on ethnoracial and
educational differences in vaccine hesitancy. I find in my sample that
Hispanic-Latinos and Asians were more likely than non-Hispanics and non-Asians
to receive or plan to receive a vaccination against COVID-19 (Table
\ref{tab:table-model-3}). Research in this area has mixed results, with some
studies showcasing consistent findings to these \citep{bagasra_etal21,king_etal21},
while others show that Whites have the lowest levels of vaccine hesitancy and
many minorities are much more hesitant \citep{momplaisir_etal21, foxworth21}. 
My finding that college-educated respondents were more likely seek vaccination is 
largely consistent with the broader literature m\citep{khairat_etal22}, though 
again there are many variations depending on the vaccine
in question and study context \citep{siddiqui_etal13}.

>>>>

Previous research has greatly failed to distinguish between the activation of
information-seeking behaviors online and offline. Using theories of 1) social
support and 2) uses and gratifications theory I investigate the factors associated
with each modality type when on information-seeking modality: personal connection,
doctor, social networking site, online forum, and online search engine. Using
novel survey data of 948 Americans and their experience seeking out
information about the COVID-19 vaccines, I find little evidence that online
search is more utilized than seeking social support from personal network
connections or health professionals. I find evidence that the modalities queried
in this survey are conceptually different and that the utilization of different
modalities varies by demography and information sources. Finally, I find that
different sources of information exposure and information search modalities hold real
world consequences through their associations with COVID-19 vaccination rates
and intentions, as information from a doctor increased the COVID-19 vaccination
uptake while receiving information from a social networking site like Facebook
or Twitter was associated with lower odds of vaccination.

@@

\hypertarget{intro-1}{%
\section{Introduction}\label{intro-1}}

@@

Information is especially important given the prominent trends of
misinformation, disinformation, and mistrust in traditional institutions
\citep{starbird19, kata10}. While no belief in false information can be thought of as
harmless \citep{douglas21} some discredited theories such as 'vaccines cause autism'
have major ramifications for both the individual and public health.
For example, a newfound public resistance to vaccination
against Measles by so-called 'anti-vaxxers' caused a 17\% increase in rates
worldwide in 2019. This increase killed  142,000 people, most of whom were
children under the age of five \citep{givetash19}. However, even in the ever-evolving
research agenda of misinformation and infodemiology \citep{eysenbach02}, much of the
research focuses on the 'push' or 'supply' side of information, like spaces where
individuals first encounter with conspiracy theories or other information
\citep{johnsonOnlineCompetitionPro2020, broniatowski_etal20}.

The lack of research in which modalities are likely to be chosen when an
individual faces a need for information makes it difficult for policy makers to
propose effective information campaigns that promote the health and wellbeing of
individuals in our society. Even outside of the misinformation literature, much
of the research conducted in social networks and communication focus on senders,
influencers, and persuasion strategies 
\citep{mertonManifestLatentFunctions1968, katzPersonalInfluencePart1955, lazarsfeldPeopleChoice1944},
rather than on “the receiver as an active information seeker and processor." 
\citep{johnsonComprehensiveModelCancerRelated1993}
\citep[for an exception, see]{eysenbach09}.

I use the case of information around COVID-19 vaccinations to explore the
variation of usage of information search modalities. In doing so, I seek to answer
how computer-mediated or interpersonal information-seeking strategies vary
across populations in their search for information about COVID-19 vaccinations
and investigate how these strategies affect vaccination uptake. Specifically, this article 
answers two research questions: (1) How do computer-mediated or interpersonal information-seeking
strategies vary across populations? (2) How does the information search modality utilized 
affect COVID-19 Vaccination uptake?

@@

However, informational support can also be sought outside of the social network
context, namely via computer-mediated information search tools such as the
process of “Googling”, or the utilization of internet search engines. 
As the online environment began penetrating all facets of
modern human life, it makes sense that performing online search has become one
of the most convenient modalities for information search. Small
\citet{smallSomeoneTalk2017} showed that Graduate students often
confided in a "miscellaneous classmates encountered down the hall" (p.
176) instead of established and trusted confidants because they
simply were there at the right time. I theorize that online search engines
may be the most frictionless and costless mode of support. 
No social capital or relationship is necessary when choosing to utilize a search engine.

There are three computer-mediated modalities I consider for this analysis: online
search engines like Google or Bing, posting questions on online forums like
subreddits or Facebook groups, and posting a status update online via Facebook
or Twitter. While the first two are largely anonymous and do not require a
personal network, the third is a unique hybrid between personal network
connections and online search.

@@

Adapting these facets of UGT and social support to my own case, I theorize that
online search allows for increased anonymity, a lowered social cost, and the
potential avoidance of embarrassment and other negative social interactions,
especially in the case on search engines. \citet{rainsCopingIllnessDigitally2018}
finds that patients tend to search for
technical information about an illness online but they then turn to their social
network for experiential information from others facing similar circumstances in
the case of cancer. The type of information sought is therefore important.
If specific expertise on a specific topic is desired by a searcher, they may
reach out to personal connections that they see as expert such as a doctor, or
if an individual distrusts the medical establishment, they may be more likely to
activate informational support among their social network or turn to online
groups that validate their worldview \citep{bogersHowSocialAre2014}. Finally, UGT and
Brasher's definition of social support \citeyearpar{brashersInformationSeekingAvoiding2002}
help us to theorize that the psychosocial needs like identity management or relational
maintenance of an individual may influence their chosen information search modality: 
when the informational need is related to forming and deepening social ties search 
is likely to be done from network ties.

@@

My analytic strategy proceeds in four steps. In Tables \ref{tab:table-1-ind}
\& \ref{tab:table-2-dep}, I present descriptive statistics for all study
variables, including variable ranges, means, and standard deviations. For this
paper, I rely heavily on logistic regression, modeled in \texttt{r}; specifically, I
fit a series of binomial generalized linear models with a logit link \citep{venables2002a},
otherwise known as logistic regression model \citep{hothorn2006handbook}.
This approach is appropriate because the data
are non-nested, cross-sectional data with binary independent variables. In Table \ref{tab:table-model-1}
\footnote{All Tables in this paper were created with the modelsummary package in \texttt{r} 
\citep{modelsummary}},I fit a logistic regression model predicting
whether someone sought information about COVID-19 using their sources of
information (`Received info') as well as various demographic variables such as
age, education level and race. Figure \ref{fig:plot-model-1} then illustrates
the relationship between the coefficients and information-seeking.\footnote{Figures 
in this paper were all created using the \texttt{r} packages jtools \citep{jtools}
and ggplot2 \citep{wickham_etal, wickham11}}.
In Table \ref{tab:model-2-phi}, I disaggregate information-seeking behaviors by
investigating the difference in proportions of each of the 5 different avenues
of seeking information about COVID-19: from another person, from a doctor, on an
online forum, on a social networking site, or using an online search tool. I
investigate these differences through a phi coefficient \citep{warrens08}, otherwise
known as a mean square contingency coefficient, which is used to investigate the
degree of association between two binary variables.\footnote{To calculate the Phi
  Coefficient, I utilize the Psych \texttt{r} package \citep{psych}} I then investigate the
associations between my predictors and the five information search modalities by
modelling a series of logistic regressions in Table \ref{tab:table-model-2}.
Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information exposure sources, information-seeking behaviors and
the choice to get vaccinated against COVID-19 through a logistic regression
model predicting Vaccination Outlook. Figure \ref{fig:plot-model-3} then
illustrates the relationship between the coefficients and vaccination outlook.

@@

\begin{figure}[h]
{\centering \includegraphics[width=0.8\linewidth]{figs/paper2/plot-model-1-1}}
\caption{What predicts someone intentionally searched for information? Plot of Coefficients}\label{fig:plot-model-1}
\end{figure}

Table \ref{tab:table-model-1} provides the results of my logistic regression
analysis predicting whether someone sought information about COVID-19. These
initial results suggest similar results for each modality of information
delivery: each mode of receiving information whether from a doctor, a person,
the news, a social networking site, or an online forum, all increase the odds of
seeking out information. For example, respondents who had received information
from a doctor or other medical professional were 2.82 (odds ratio = \(exp(\beta k)\),
\emph{p} \textless{} 0.001) times more likely to seek out information over someone
who had not. Similarly, respondents who had received information from `a
person like friend, neighbor, or family member that [they] know' were 1.87
(\emph{p} \textless{} 0.001) times more likely to seek out information over 
someone who had not received information from a person like that. Interesting, 
those who had received information from an online discussion group, listserv,
or other online forum including a Facebook group or subreddit were 2.39 (\emph{p}
\textless{} 0.001) times more likely to search out more information than 
someone who had not. While most demographic variables do not seem to have a 
strong effect on whether someone sought out information about the COVID-19 
vaccine, a few key variables had strong associations.  Respondents who are 
older are more likely to seek information; The odds are about 3\% higher when 
age is equal to x + 1 relative to x, possibly indicating a generational effect
of information-seeking patterns (\emph{p} \textless{} 0.01). Additionally,
those who were more educated, that is those with an Associate's degree or higher,
were 1.58 more likely to seek additional information than those without the degree
(\emph{p} \textless{} 0.05). And finally, there is evidence to suggest that the Black or
African American sample was more likely to seek out information, specifically:
Blacks were 3.58 times more likely to seek out information over non-Blacks (\emph{p}
\textless{} 0.05). Figure \ref{fig:plot-model-1} illustrates the relationship
between the coefficients and information-seeking.

\hypertarget{information-search-modalities}{%
\subsection{Information Search Modalities}\label{information-search-modalities}}

@@

To further investigate how people search for information, I asked those who had
sought information out intentionally, ``How did you look for information about
the COVID-19 vaccine?'' Because respondents could select as many responses as
applicable, each response is recorded as a dichotomous variable. Table
\ref{tab:table-1-ind} reveals differences in the prevalence of usage of the
various information-seeking modalities: Around 40\% of the sample has inquired for
information from a doctor, a person, or using online search tool (44\%, 42\%, 41\%), while my
respondents used modalities like online forums (27\%) and social networking sites (18\%)
to seek out information at significantly lower rates.

To investigate how each
Information Search modality are related to each other using the Phi Coefficient
($\phi$) of binary association between each Information Search modality pair.
The Phi coefficient can be interpreted like a correlation coefficient, with
numbers closer to -1 indicating a very strong negative relationship and those closer to 
positive 1 indicating a very strong positive relationship
(Warrens 2008). Table \ref{tab:model-2-phi} shows the results of these
coefficients. Out of the five information search modalities investigated, there is
evidence that the modalities are distinctly different concepts because most
coefficients fall under 0.3, the general cutoff for correlation
coefficients to indicate a relationship. There does seem to be a relationship
between Online Forums and social networking sites, possibly due to an
individual's latent propensity to use online networks over in-person networks. These
coefficients indicate a weak relationship between any two modalities of
information search and that respondents in my sample utilize each of these a
little bit differently.

I find that indeed the most common modalities are 
asking a doctor, asking a friend, and asking a search engine which confirms
Hypthesis \ref{hyp:drgooglefriend}. However, because the modalities 95\% confidence intervals 
in Table \ref{tab:table-1-ind}
are overlapping, I fail to find evidence for Hypothesis \ref{hyp:online-vs-network},
that using an online search engine was more commonplace than asking a friend.

@@

I conduct a separate logistic regression for each search modality in Table \ref{tab:table-model-2}. 
Modeling each response as a separate formula is useful for interpretation, but
there are important caveats: because each logistic regression is on a different
scale, one must not compare the magnitude of coefficients between models. We
can, however, use the direction and significance of the coefficients to draw
conclusions about these different forms of information search modalities.

The first model in Table \ref{tab:table-model-2} predicts whether a
respondent sought information intentionally about COVID-19 vaccinations by
asking their doctor or another health professional. First and foremost, I find
that those who received information about COVID-19 vaccinations were
6.97 times more likely to seek out more information from their doctor than those who had
not (\emph{p} \textless{} 0.001). However, receiving information from other modalities also
increased the odds of seeking out information from medical professions. Those who
received information from a person such as a friend or a relative were
2.23 times more likely to ask their doctor (\emph{p} \textless{} 0.001), while those who received
information from the news or television were 1.55 times more likely (\emph{p} \textless{} 0.01). 
I also find that those who received information from an online forum like a subreddit were 51\% 
more likely to ask their doctors than those who had not (\emph{p} \textless{} 0.05). 
Finally, respondents with an Associate's degree or higher were 72\%
more likely to ask their doctor for information on the COVID-19 vaccinations
than those who held less education (\emph{p} \textless{} 0.01).

@@

Searching for information using an online search engine such as Google or Bing
is theoretically the search modality with the least amount of social or cognitive
friction. Our descriptive statistics showed that not everyone used this modality,
with only 41\% of our sample (See Table \ref{tab:table-1-ind}) having sought
information about the COVID-19 vaccines using online search engines. My model
reveals interesting patterns to help explain the variation. As with previous
models, receiving information of any kind increase the odds of online search,
though to varying magnitudes (Doctor: 1.54 odds; Person: 1.44 odds; News or Television: 2.98 odds; 
social networking site: 3.57 odds; Online Forum: 2 odds). I also find that older respondents
were more likely to search online, with each addition year aged to yield 3\%
higher odds of searching online (\emph{p} \textless{} 0.001). The most interesting variations
come from what decreases the odds of online search. First, those with an
Associate's degree or higher were 61\%
less likely to search online for questions about COVID-19 than those with less
educational attainment (\emph{p} \textless{} 0.001). In addition, I find that Hispanic-Latinos
had 44\% lower odds of searching online than non-Hispanics (\emph{p} \textless{} 0.05).

@@

Finally, in Table \ref{tab:table-model-3}, I investigate whether there is a
relationship between information receiving and information-seeking behaviors and
the choice to get vaccinated against COVID-19 through a logistic regression
model predicting Vaccination Outlook. I find that receiving information from a
doctor or other medical profession is associated with 2.85 odds of choosing
to receive a COVID-19 vaccination (\emph{p} \textless{} 0.001) and that seeking 
information from a doctor also increases the odds of vaccination by 4 (\emph{p} \textless{} 0.001).
I find that my respondents who received information on a social networking site
like Facebook or Twitter about the vaccines were 55\%
\textbf{less likely} to choose to get vaccinated than those who received no information through
that modality (\emph{p} \textless{} 0.001). However, I did find that those who reached out to
family or friends with their concerns were 77\% more likely to become vaccinated 
(\emph{p} \textless{} 0.05). Furthermore, my respondents who held an Associate's degree
or above had 3.6 higher odds of becoming immunized (\emph{p} \textless{} 0.001).
And finally, I found further ethnoracial differences in my sample. I found that
Hispanic-Latinos had 2.83 higher odds of vaccination than non-Hispanics
(\emph{p} \textless{} 0.05) and that my Asian sample had 4.73 higher odds as well over
non-Asians (\emph{p}  = 0.09). See Figure \ref{fig:plot-model-3} for a visual
representation of how these different coefficients are related to vaccination outlook.

@@

Previous research in Sociology and Infodemiology has greatly failed to
distinguish between the activation of information-seeking behaviors online and
offline. In this paper, I sought to uncover just how different various methods of
information search are and begin a line of research inquiry that investigates
the factors associated with each different modality. Finally, I also uncovered
how the different sources of information exposure and information search
modalities hold real world consequences through their associations with COVID-19
vaccination rates and intentions.

@@

Table \ref{tab:table-model-2} further demonstrated important takeaways about
how individuals seek information. First, I find that the different information
seeking modalities queried in this survey are conceptually different and that the
utilization of different varies by demographic and information exposure source. 
Overall, being exposed to information about COVID-19 vaccinations from any 
source is associated with information-seeking behaviors,
though there are key variations. First, if one received information from a
doctor, they were likely to search from information from a doctor; this may
indicate an already existing trusting relationship between patient and
healthcare provider but it may also indicate the healthcare provider taking
initiative and emphasizing the importance of the vaccine or the survey respondent
seeking out information from an expert. Another important finding is that if you
received information from a social networking site like Facebook or Twitter, you
were less likely to query Online Forums like Reddit or Facebook Groups; this may
be an example of Uses and Gratification Theory
\citep{blumlerUsesMassCommunications1974}, where the two online platforms may act as
substitute sources of information and those who were satisfied with the
information they received on a social networking site didn't have the need to
seek out more information. Finally, the ethnoracial variations exhibited in
Table \ref{tab:table-model-2} likely demonstrate how cultural attitudes around
the trustworthiness of different sources of information affect the utilization
of different methods; for example, Asians seem are less likely to use online
forums than non-Asians, while Hispanics are more likely to use them than
non-Hispanics. The internal variations between the different information search
modalities hint at different user profiles and may have major repercussions on the
quality of information they find and who is exposed to poor quality information.

Given the rampant misinformation around COVID-19, its related vaccinations
\citep{pathakInfodemicsCOVID19Role2020, mottaHowRightLeaningMedia2020, shahsavariConspiracyTimeCorona2020},
and the slowed rate of vaccinations in the
United States, it is important to uncover what relationship the different
sources of information exposure and information search modalities for COVID-19 vaccinations
are associated with compliance with public health recommendations. Table
\ref{tab:table-model-3} demonstrated just how these different sources of information 
exposure and information search modalities are associated with real world
consequences through COVID-19 vaccination rates and intentions. The first
takeaway is that receiving or seeking information from a doctor or other medical
profession was associated with higher likelihood of completed or planned vaccinations.
While blanket advice like ``Healthcare Providers should recommend the vaccine to
their patients'' would be ineffective because of the declining number of
Americans with a primary care doctor \citep{levine_etal20}, increasing trust in the
institution of medicine seems to remain a strong predictor of vaccinations.
A second major takeaway is that receiving information from a Social Networking
Site like Facebook timeline or Twitter status update was significantly
associated with lower vaccination rates. While we do not know what exact
information was absorbed on these platforms, the lower odds of vaccination
indicate that it was not positive. Much has been attempted between 2020 and 2022
to curb vaccine misinformation on these social networking platforms 
\citep[see][for an early example]{bowman20}; however, I find evidence that these social
networking platforms nevertheless have a measurable negative impact. Finally,
this study also contributes to the conversation on ethnoracial and
educational differences in vaccine hesitancy. I find in my sample that
Hispanic-Latinos and Asians were more likely than non-Hispanics and non-Asians
to receive or plan to receive a vaccination against COVID-19 (Table
\ref{tab:table-model-3}). Research in this area has mixed results, with some
studies showcasing consistent findings to these \citep{bagasra_etal21,king_etal21},
while others show that Whites have the lowest levels of vaccine hesitancy and
many minorities are much more hesitant \citep{momplaisir_etal21, foxworth21}. 
My finding that college-educated respondents were more likely seek vaccination is 
largely consistent with the broader literature m\citep{khairat_etal22}, though 
again there are many variations depending on the vaccine
in question and study context \citep{siddiqui_etal13}.
